---
title: "hw1"
author: "Xinyuan Liu"
date: "2021/9/22"
output: github_document

---

# Problem 1

```{r Problem 1, message=FALSE}
library(tidyverse)
problem1_df <- tibble(
  sample = rnorm(10), ## random sample of size 10 from a standard Normal distribution
  gr_than_0 = sample > 0, ## indicating whether elements of the sample are greater than 0
  vec_char = c("X", "i", "n", "y", "u", "a", "n", "L", "i", "u"), ##character vector with length = 10
  vec_factor = c("high", "high", "high", "middle", "middle", "middle", "low", "low", "low", "middle")  ## factor vector of length 10 with 3 levels 
)
mean(pull(problem1_df, var = 1))
mean(pull(problem1_df, var = 2))
mean(pull(problem1_df, var = 3))
mean(pull(problem1_df, var = 4))
## These try to compute the mean of numbers in each column
```

We could only get the mean for the sample because it is the only numeric variable.

```{r as.numeric, echo = TRUE, eval = FALSE}
as.numeric(pull(problem1_df, var = 2))
as.numeric(pull(problem1_df, var = 3))
as.numeric(pull(problem1_df, var = 4))
## These try to convert the non-numeric variables into numeric ones
```

In this case, the logical vector is able to become numeric but the character vector and factor vector are not able to be transferred into numerical variable

# Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

The dataset "penguins" has different columns whose names are : `r names(penguins)`. 

It has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r penguins_scatterplot, message=FALSE}
pg_df <- tibble(
  x = penguins$bill_length_mm, ## x is the bill length in mm
  y = penguins$flipper_length_mm ## y is the flipper length in mm
) ## This is the data frame of bill and flipper variable in the penguin dataset

ggplot(pg_df, aes(x = x, y = y, color = penguins$species)) + geom_point() ## This gives a scatterplot where x shows penguins' bill length and y shows penguins' flipper length, and colors differentiates different species of penguins 

ggsave("scatter_plot.pdf")
```
